\section*{Introduction}

CBo is a C executable to check code formatting.\\

It is intended to work on various languages but is currently implemented only for C. The rules it inforces are personally defined and its use is currently purely personal.\\

It uses the \begin{ttfamily}PBErr\end{ttfamily}, \begin{ttfamily}GSet\end{ttfamily}, \begin{ttfamily}ResPublish\end{ttfamily} and \begin{ttfamily}PBCExtension\end{ttfamily} libraries.\\

\section{Interface}

\begin{scriptsize}
\begin{ttfamily}
\begin{lstlisting}
cbo
[-help] : print the help message
[-listFile] : print only the list of file(s) with error(s)
\end{lstlisting}
\end{ttfamily}
\end{scriptsize}

CBo must be used after the commpilation phase. It works on the assumption that the code is correct, i.e. it compiles with no error.\\

\section{Rules}

\subsection{C language}

\subsubsection{LineLength}

Rule:
\emph{Lines must be less than or equal to 79 characters long.}

\subsubsection{TrailingSpace}

Rule:
\emph{There must be no spaces or tabs at the end of the lines.}

\subsubsection{EmptyLineBeforeClosingCurlyBrace}

Rule:
\emph{There must be an empty line before a line continaing a closing curly brace.}

\subsubsection{EmptyLineAfterOpeningCurlyBrace}

Rule:
\emph{There must be an empty line after a line containing an opening curly brace.}

\subsubsection{EmptyLineAfterClosingCurlyBrace}

Rule:
\emph{There must be an empty line after a line containing a closing curly brace.}

\subsubsection{SpaceAroundComma}

Rule:
\emph{There must be a space after a comma but not before.}

\subsubsection{SpaceAroundSemicolon}

Rule:
\emph{There must be no space before a semicolon.}

\subsubsection{SpaceAroundOperator}

Rule:
\emph{There must be a space around the operators + - / \textbar .}

\subsubsection{SeveralBlankLine}

Rule:
\emph{There must be no several successive blank lines.}

\subsubsection{NoCurlyBraceAtHead}

Rule:
\emph{There must be no line starting with an opening curly brace if its closing curly brace is not on the same line.}

\subsubsection{NoCurlyBraceAtTail}

Rule:
\emph{A closing curly brace must be alone on its line except if its opening curly brace is on the same line.}

\subsubsection{CharBeforeDot}

Rule:
\emph{A dot must be surrounded by [a-zA-Z0-9] or be at the head of a line.}

\subsubsection{SpaceBeforeOpeningCurlyBrace}

Rule:
\emph{There must be a space or an opening curly brace before an opening curly brace.}

\subsubsection{EmptyLineBeforeComment}

Rule:
\emph{There must be an empty line before a comment line.}

\subsubsection{IndentLevel}

Rule:
\emph{Blocks must be indented with an indentation level of 2 spaces.}

\subsubsection{SeveralArgOnOneLine}

Rule:
\emph{There must be no several arguments on the same line when doing function call.}

\subsubsection{ArgumentsUnaligned}

Rule:
\emph{Arguments of functions must be aligned on the first character of their variable name.}

\subsubsection{IndentTab}

Rule:
\emph{Blocks must be indented with spaces.}

\subsubsection{EmptyLineBeforeCase}

Rule:
\emph{There must be an empty line before 'case' and 'default' in 'switch' blocks.}

